Measuring individual differences in the understanding of gaze cues

### 2021-12-18 paper/manuscript.Rmd
change title and add idea for opener

---
title             : "Measuring individual differences in the understanding of gaze cues"
shorttitle        : "Gaze cue understanding"

@@

>>>>

---
title             : "Measuring individual differences in the understanding of gaze cues across the lifespan"
shorttitle        : "Gaze cue understanding"

@@

Idea for an opener :)

Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences. For example ... .
